\subsection{Abstract Algebra}

\question Let $SL_2(\mathbb{Z})$ denote the group. Let $H$ be the subgroup of $SL_2(\mathbb{Z})$ consisting of those matrix such that
\begin{itemize}
    \item the diagonal entries are all equivalent to $1\mod{3}$,
    \item the off diagonal entries are all divisible by 3.
\end{itemize}
What is the index of $H$ in $SL_2(\mathbb{Z})$.

\begin{solution}
    Given that $H=\left\{A\in SL_2(\mathbb{Z}): A\cong I\mod(3)\right\}$. Define $\phi:SL_2(\mathbb{Z})\to SL_2(\mathbb{Z}_3)$ to be the natural reduction map i.e.,
    $$\phi\left(\begin{pmatrix}a&b\\c&d\end{pmatrix}\right)=\begin{pmatrix}a+3\mathbb{Z}&b+3\mathbb{Z}\\c+3\mathbb{Z}&d+3\mathbb{Z}\end{pmatrix}.$$
    Then $\left|\frac{SL_2(\mathbb{Z})}{\ker{\phi}}\right|=\left|SL_2(\mathbb{Z}_3)\right|$. One can easily verify that $\ker{\phi}=H$. Thus
    $$\left|\frac{SL_2(\mathbb{Z})}{H}\right|=\left|SL_2(\mathbb{Z}_3)\right|=\frac{(3^2-1)(3^2-3)}{3-1}=24.$$
\end{solution}

\question Let $\alpha:G\to G_1$ and $\beta:G\to G_2$ be group homomorphisms.
\begin{itemize}
    \item Show that if $\ker{\alpha}\subseteq\ker{\beta}$ and $\alpha$ is surjective then there is a well-defined homomorphism $\phi:G_1\to G_2$ such that $\beta=\phi\circ\alpha$.
    \item Show that if $\ker{\alpha}\nsubseteq\ker{\beta}$ then there is no such homomorphism $\phi$.
\end{itemize}
\begin{solution}
    Let $y\in G_1$. Since $\alpha$ is surjective, there exists $x\in G$ such that $\alpha(x)=y$. Now define $\phi:G_1\to G_2$ by $\phi(y)=\beta(x)$ where $\alpha(x)=y$. Let $y_1,y_2\in G_1$ such that $y_1=y_2$. Then there exists $x_1,x_2\in G$ such that $\alpha(x_1)=y_1$ and $\alpha(x_2)=y_2$. Now $\alpha(x_1-x_2)=0$ which implies that $x_1-x_2\in\ker{\phi}$. But $\ker{\alpha}\subseteq\ker{\beta}$, so $x_1-x_2\in\ker{\beta}$ and hence $\beta(x_1)=\beta(x_2)$. Again for $y_1,y_2\in G_1$, let $\alpha(x_1)=y_1$ and $\alpha(x_2)=y_2$ then $\alpha(x_1x_2)=y_1y_2$. Now,
    $$\phi(y_1y_2)=\beta(x_1x_2)=\beta(x_1)\beta(x_2)=\phi(y_1)\phi(y_2).$$
    Thus $\phi$ is a homomorphism. And for any $x\in G$, $\phi(\alpha(x))=\beta(x)$.\\
    Now assume that $\ker{\alpha}\nsubseteq\ker{\beta}$. To the contrary assume that such a $\phi$ exists. Let $x\in\ker{\alpha}$ then $\alpha(x)=0$ and so $\beta(x)=\phi\circ\alpha(x)=\phi(\alpha(x))=\phi(0)=0$. That is, $\ker{\alpha}\subseteq\ker{\beta}$. $\Rightarrow\Leftarrow$
\end{solution}

\question Prove of give counterexample: For every $\sigma\in A_5$ there is a $\tau\in S_5$ such that $\tau^2=\sigma$.

\begin{solution}
    Let $\sigma$ be an element in $A_5$. If $\sigma$ is of odd order say $2k+1$ for some $k$ then $\sigma^{2k+1}=e$ or $\sigma=\sigma^{-2n}=(\sigma^{-k})^2$. Now assume that order of $\sigma$ is even. Only element in $A_5$ of even order is of the form $(ab)(ad)$ which is square of $(abcd)$. 
\end{solution}

\question Let $G$ be a finite group and suppose that $G\times G$ has exactly four normal subgroups. Show that $G$ is simple and nonabelian.

\begin{solution}
    
\end{solution}

\question Prove that $\Q$, can not be written as a direct sum of two non trivial subgroups.

\question Let G and H be finite groups of relatively prime. Show that $\Aut(G\times H)$, the group of automorphisms of $G\times H$, is isomorphic to the direct product of $\Aut(G)$ and $\Aut(H)$.

\question[8B, Fall14] Determine, up to isomorphism, all finite groups $G$ such that $G$ has exactly three conjugacy classes.
\begin{solution}
    The singleton set containing identity element is a conjugacy class of $G$. Let $r$ and $s$ be the size of other two conjugacy classes then $|G|=1+r+s$. This imples that $r|s+1$ and $s|r+1$. WLOG assume that $r\leq s$. Then $s|r+1$ implies that $s=r=1$ or $s=r+1$. Since $r|s+1$, thus $s=r+1$ implies that $r|r+2$ i.e. $r=1$ or $r=2$. Therefore the possible values of $(r,s)$ are $(1,1), (1,2)$ and $(2,3)$. Now $r=s=1$ implies $|G|=3$ thus $G\cong\mathbb{Z}_3$. $r=1,s=2$ implies $|G|=4$. But any group of order 4 is abelian which contradict the fact that $G$ has a conjugacy class of size $2$. $r=2,s=3$ implies $|G|=6$. In this case $G$ can not be abelian and there is up to isomorphismonly one non abelian group of order 6 so $G\cong S_3$. 
\end{solution}

\question[8B, Sp16] Factor the polynomial
$$f(x)=6x^5+3x^4-9x^3 +15x^2-13x-2$$
into a product of irreducible polynomials in the ring $\Q[x]$.
\question[9B, Sp16] Let $p$ be a prime number. Prove that every group $G$ of order $p^2$ is commutative.