\section{For Exams}

\question[Fa82] \begin{enumerate}
    \item There is no continuous map from $[0,1]$ onto $(0,1)$.
    \item There exists continuous map from $(0,1)$ onto $[0,1]$.
    \item There is no continuous bijection from $(0,1)$ onto $[0,1]$.
\end{enumerate}

\question[Fa93] Let $f$ be a continuous real valued function on $[0,\infty)$. Let $A$ be the set of real numbers $a$ that can be expressed as $a=\lim_{n\to\infty}{f(x_n)}$ for some sequence $(x_n)$ in $[0,\infty)$ such that $\lim_{n\to\infty}{x_n}=\infty$. Prove that if $A$ contains the two numbers $a$ and $b$, then contains the entire interval with endpoints $a$ and $b$.

\question[Su78] Let $f:\R\to\R$ be continuous. Suppose that $\R$ contains a countably infinite subset $S$ such that
$$\int_{p}^{q}{f(x)dx}=0$$
if $p$ and $q$ are not in $S$. prove that $f$ is identically 0.

\question[Sp93] Let $f$ be a real valued $C^1$ function on $[0,\infty)$ such that the improper integral $\int_{1}^{\infty}{|f'(x)|dx}$ converges. Prove that the infinite series $\sum_{n=1}^{\infty}{f(n)}$ converges if and only if the integral $\int_{1}^{\infty}{f(x)dx}$ converges.

\question[Fa01] let $S$ be the set of continuous real-valued functions on $[0,1]$ such that $f(x)$ is rational whenever $x$ is rational. Prove that $S$ is uncountable.

\question[fa00] Let $f:\R\to\R$ be uniformly continuous with $f(0)=0$. Prove that there exists a positive number $B$ such that $|f(x)|\leq 1+B|x|$, for all $x$.

\question[Fa78] Let $f:\R\to\R$ is monotonically increasing. prove that the set where $f$ is not continuous is finite or countably finite.

\question[Su83] Prove that a continuous function from $\R$ to $\R$ which maps open sets to open sets be monotonic.

\question[fa91] Let $f$ be a continuous function from $\R$ to $\R$ such that $|f(x)-f(y)|\geq|x-y|$ for all $x$ and $y$. Prove that the range of $f$ is all of $\R$.

\question[Fa81] let $f$ be a continuous function on $[0,1]$. Then prove that
\begin{enumerate}
    \item $$\lim_{n\to\infty}{\int_{0}^{1}{x^nf(x)dx}}=0.$$
    \item $$\lim_{n\to\infty}{n\int_{0}^{1}{x^nf(x)dx}}=f(1).$$
\end{enumerate}

\question[Sp89] Let $f$ be a continuous real valued function defined on $[0,1]\times[0,1]$. Let the function $g$ on $[0,1]$ be defined by
$$g(x)=\max\{f(x,y): y\in[0,1]\}.$$
Prove that $g$ is continuous.

\question[Fa01] Let the function $f:\R\to\R$ be bounded on bounded sets and have the property that $f^{-1}(K)$ is closed whenever $K$ is compact. Prove $f$ is continuous.

\question[Su83] Let $b_1, b_2,\ldots$ be positive real numbers with
$$\lim_{n\to\infty}{b_n}=\infty,\,\,\,\text{and}\,\,\,\,\lim_{n\to\infty}{\left(\frac{b_n}{b_{n+1}}\right)}=1.$$
Assume also that $b_1<b_2<b_3<\cdots$. Show that the set of quotients $\left(\frac{b_m}{b_n}\right)_{1\leq n<m}$ is dense in $(1,\infty)$.

\question[Su80, Sp97] For each $(a,b,c)\in\R^3$, consider the series
$$\sum_{n=3}^{\infty}{\frac{a^n}{n^b(\log{n})^c}}.$$
Determine the values of $(a,b,c)$ for which the series
\begin{enumerate}
    \item converges absolutely;
    \item converges but not absolutely;
    \item diverges.
\end{enumerate}

\question[Sp91] Let $A$ be the set of positive integers that do not contain the digit $9$ in their decimal expansions. Prove that $$\sum_{a\in A}{\frac{1}{a}}<\infty;$$
that is, $A$ defines a convergent subseries of the harmonic series.

\question[Su83] Let $f:[a,b]\to\R$ be a continuous function such that $f'(x)=0$ for all $x\in (a,b)$. Then $f(b)=f(a)$.

\question[Fa90] Suppose $f$ is a continuous rea valued function. Show that $$\int_{0}^{1}{f(x)x^2\,dx}=\frac{1}{3}f(\xi)$$
for some $\xi\in[0,1]$.

\question[Su81] Let $f:\R\to\R$ be continuous, with $$\int_{-\infty}^{\infty}{|f(x)|\,dx}<\infty.$$
Show that there is a sequence $(x_n)$ such that $x_n\to\infty$, $x_nf(x_n)\to 0$, and $x_nf(-x_n)\to 0$ as $n\to 0$.

\question[Fa85] let $0\leq a\leq 1$ be given. Determine all nonnegative continuous functions $f$ on $[0,1]$ which satisfy the following three conditions:
\begin{align*}
    \int_{0}^{1}{f(x)\,dx}&=1,\\
    \int_{0}^{1}{xf(x)\,dx}&=a,\\
    \int_{0}^{1}{x^2f(x)\,dx}&=a^2.
\end{align*}

\question[Fa83] let $f:[0,\infty)\to\R$ be a uniformly continuous function with the property that $$\lim_{b\to\infty}{\int_{0}^{b}{f(x)\,dx}}$$
exists. Show that $$\lim_{x\to\infty}{f(x)}=0.$$

\question[Sp83] Let $f:\R_+\to\R_+$ be a monotone decreasing function, defined  on the positive real numbers with $$\int_{0}^{\infty}{f(x)\,dx}<\infty.$$
Show that $$\lim_{x\to\infty}{xf(x)}=0.$$

\question[Fa90, Sp97] Let $f$ be a continuous real valued functions satisfying $f(x)\geq 0$, for all $x$, and $$\int_{0}^{\infty}{f(x)\,dx}<\infty.$$
Prove that $$\frac{1}{n}\int_{0}^{n}{xf(x)\,dx}\to 0$$ as $n\to\infty$.

\question[Fa84] Show that if $f$ is a homeomorphism of $[0,1]$ onto itself, then there is a sequence $\{p_n\}$, $n=1,2,3,\ldots$ of polynomials such that $p_n\to f$ uniformly on $[0,1]$ and each $p_n$ is a homeomorphism of $[0,1]$ onto itself.

\question[Fa82] Let $f_1, f_2, \ldots$ be continuous functions on $[0,1]$ satisfying $f_1\geq f_2\geq\cdots$ and such that $\lim_{n\to\infty}{f_n(x)}=0$ for each $x$. Must the sequence $\{f_n\}$ converges to 0 uniformly on $[0,1]$? (Y)

\question[Sp95] Prove that the sequence of function $f_n:\R\to\R$ define by $f_n(x)=\cos{nx}$ has no uniformly convergent subsequence.

\question[Sp01] Let the functions $f_n:[0,1]\to[0,1]$ satisfy $|f_n(x)-f_n(y)|\leq |x-y|$ whenever $|x-y|\geq 1/n$. Prove that the sequence $\{f_n\}_{n=1}^{\infty}$ has a uniformly convergent subsequence.

\question[Sp88] Does there exist a continuous real valued function $f(x)$, $0\leq x\leq 1$, such that $$\int_{0}^{1}{xf(x)\,dx}=1\,\,\,\text{and}\,\,\,\int_{0}^{1}{x^nf(x)\,dx}=0$$
for $n=0,2,3,4,\ldots$?
\begin{solution}
    $\displaystyle\int_{0}^{1}{x^nf(x)\,dx}=0$ for $n=2,3,4,\ldots$ implies that $\displaystyle\int_{0}^{1}{(x^2f(x))x^{t}\,dx}=0$ for $t=0,1,2,3,\ldots$. By Stone-Weierstress Theorem we have $x^2f(x)=0$ for all $x$, so $f\equiv 0$. Which contradicts that $\displaystyle\int_{0}^{1}{xf(x)\,dx}=1$.
\end{solution}

\question[Su82] Let $f:[0,\pi]\to\R$ be continuous and such that
$$\int_{0}^{\pi}{f(x)\sin{nx}\,dx}=0$$
for all integers $n\geq 1$. Is $f$ identically 0?

\question[Sp86] Let $f$ be a continuous real valued function on $\R$ such that
$$f(x)=f(x+1)=f(x+\sqrt{2})$$
for all $x$. Prove that $f$ is constant.

\question[Su79] Let $U\subset\R^n$ be an open set. Suppose that the map $h:U\to\R^n$ is a homeomorphism from $U$ onto $\R^n$, which is uniformly continuous. Prove that $U=\R^n$.

\question[Sp78] Prove that a map $g:\R^n\to\R^n$ is continuous only if its graph is closed in $\R^n\times\R^n$. Is the converse true?
\begin{solution}
    Converse is false. Take $n=1$ and consider the function $g:\R\to\R$ defined by
    $$g(x)=\begin{cases}
        \frac{1}{x},\,\,\,&x\neq 0\\
        0,& x=0
    \end{cases}$$
\end{solution}

\question[Fa78] Let $W\subset\R^n$ be an open connected set and $f$ a real valued function on $W$ such that all partial derivatives of $f$ are 0. Prove that $f$ constant.

\question[Sp92, Fa99] Show that every infinite closed subset of $\R^n$ is the closure of a countable set.